Instructions for ACL 2020 Proceedings

### 2019-12-05 reports/ACL2020 Paper/acl2020-paper.tex
Update structure and Experiment 1

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{graphicx}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

@@

One important dialogical feature missing from text data is laughter.
In the Switchboard dialogue corpus, laughter appears in approximately \%X of utterances.
Laughter also relates to the discourse structure of dialogue. 
Laughables.
Also useful for predicting DAs (is that already a result?)

@@

\section{Related work} % add references first
Dialogue act recoginition
\begin{itemize}
  \item \citet{pragstVectorRepresentationUtterances2018} -- dialogue vector models. Uses vector-manual DA tag correspondance to argue for semantic relevance of their vector models (related to how we use DA tagging to verrify BERT usefulness)
  \item \citet{cerisaraEffectsUsingWord2vec2017} -- standard pre-trained word embeddings do not help for DAR in any of three tested languages (English, French, Czech)
  \item \citet{kalchbrennerRecurrentConvolutionalNeural2013} -- DAR model similar to our architecture. Uses an RNN ``discourse model'' and a CNN similar to our baseline encoder
  \item \citet{khanpourDialogueActClassification2016} -- Deep LSTM utt representation. No notion of context. Finds word vectors are useful.
  \item \citet{tranPreservingDistributionalInformation2017} -- Sequential DA prediction with uncertainty propegation
  \item \citet{chenDialogueActRecognition2017} -- SOTA? SWDA DAR using attention and CRF over utterances
  \item \citet{ortegaNeuralbasedContextRepresentation2017} -- SWDA DAR with attention-based context representations and CNN utterance representations
  \item \citet{shenNeuralAttentionModels2016} -- Uses attention for utt encoding in DAR. No notion of context, I think.
  \item \citet{tranHierarchicalNeuralModel2017} -- RNNs at both the utteranec and dialogue level. Also attention. Very similar to our architecture.
\end{itemize}

@@

We employ a simple DAR model with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (figure \ref{fig:model-architecture}).
Since we are primarily interested in comparing different utterance encoders, we use a simple RNN as the sequence model in every configuration. 
The RNN takes the encoded utterance as input at each time step
Its hidden state is passed to a simple linear classification layer over dilague act tags.
Conceptually, the encoded utterance represents the context-agnostic semantic content of the utterance, and the hidden state of the RNN represents the discourse context.

@@

For the BERT utterance encoder, we use the BERT-BASE model with hidden size of 768 and 12 transformer layers and self-attention heads \citep[][see \S3.1]{devlinBERTPretrainingDeep2018}.
We use the un-cased model implemenetd by \citet{wolfHuggingFaceTransformersStateoftheart2019}.

@@

\section{Experiments}
\subsection{Experiment 1: Impact of laughter} \label{sec:experiment1}   % Vlad
In the first experiment we investigated whether laughter, as an example of a dialogue-specific signal, is a helpful feature for DAR.
Therefore, we train another version of each model: one containing laughters (L) and with laughters left out (NL), and compare their performances in DAR task.
From the results (see Table~\ref{tab:laughter}) we can conclude that .
\begin{table}
  \label{tab:laughter}
  \centering
  \begin{tabular}{@{}lll@{}}
    \toprule
                      & SWDA  & AMI-DA \\ \midrule
    \texttt{BERT-NL}  & 77.07 & 67.06       \\ 
    \texttt{BERT-L}   & 76.93 & 67.12       \\ \midrule
    \texttt{CNN-NL}   & 75.08 & 63.46        \\
    \texttt{CNN-L}    & 75.40 & 64.30        \\ \bottomrule

  \end{tabular}
  \caption{Comparison of models depending on using laughter in training phase.}
\end{table}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{img/SWDA-bertLvsNL.pdf}
  \caption{Change in accuracy for each SWDA dialogue act. Positive changes when adding laughter are shown in blue. Vertical bars indicate how often dialogue act is associated with laughter.}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{img/AMI-DA-bertLvsNL.pdf}
  \caption{Change in accuracy for each AMI dialogue act. Positive changes when adding laughter are shown in blue. Vertical bars indicate how often dialogue act is associated with laughter.}
\end{figure*}
% TODO per dialogue act analysis
% DONE compare impacts of CNN vs BERT
% DONE for both AMI and SWDA
% ?

@@

\subsection{Experiment 4: Cross-domain pre-training (if time permits)} \label{sec:experiment4} % Bill
%  - cross-domain pre-training

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

@@

One important dialogical feature missing from text data is laughter.
In the Switchboard dialogue corpus, laughter appears in approximately \%X of utterances.
Laughter also relates to the discourse structure of dialogue. 
% Laughables.
Also useful for predicting DAs (is that already a result?)

@@

@@

We employ a simple DAR model with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (figure \ref{fig:model-architecture}).
Since we are primarily interested in comparing different utterance encoders, we use a simple RNN as the sequence model in every configuration. 
The RNN takes the encoded utterance as input at each time step
Its hidden state is passed to a simple linear classification layer over dialogue act tags.
Conceptually, the encoded utterance represents the context-agnostic semantic content of the utterance, and the hidden state of the RNN represents the discourse context.

@@

For the BERT utterance encoder, we use the BERT-BASE model with hidden size of 768 and 12 transformer layers and self-attention heads \citep[][see \S3.1]{devlinBERTPretrainingDeep2018}.
We use the un-cased model implemented by \citet{wolfHuggingFaceTransformersStateoftheart2019}.

@@

\section{Experiments}
\subsection{Experiment 1: Impact of laughter} \label{sec:experiment1}   % Vlad
In the first experiment we investigated whether laughter, as an example of a dialogue-specific signal, is a helpful feature for DAR.
Therefore, we train another version of each model: one containing laughs (\texttt{L}) and one with laughs left out (\texttt{NL}), and compare their performances in DAR task.
Table~\ref{table:laughter-total-acc}) compares the results from applying the models with two different different utterance encoders (\texttt{BERT}, \texttt{CNN}). From observing the total accuracy scores, models appear to be almost unaffected by leaving out the laughters. On the other hand, we can observe differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:swda-by-da} for Switchboard and Figure~\ref{fig:ami-by-da} for AMI corpus).

In order to further investigate the differences we have grouped dialogue acts in Switchboard according to DAMSL coders manual \citep{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}. Different DA groups containing 
\begin{table}
  \centering
  \begin{tabular}{@{}lll@{}}
    \toprule
                      & SWDA  & AMI-DA   \\ \midrule
    \texttt{BERT-NL}  & 77.07 & 67.06       \\ 
    \texttt{BERT-L}   & 76.93 & 67.12       \\ \midrule
    \texttt{CNN-NL}   & 75.08 & 63.46        \\
    \texttt{CNN-L}    & 75.40 & 64.30        \\ \bottomrule

  \end{tabular}
  \caption{Comparison of models depending on using laughter on the training phase. }
  \label{table:laughter-total-acc}
\end{table}

\begin{table}
  \label{tab:laughter}
  \centering
  \begin{tabular}{@{}lccc@{}}
    \toprule
    & \%lassoc & \%L  & $\Delta$ (mean acc.) \\ \midrule
    Forward-CF & 11.86 & 4.59 & 11.40\\
    Backward-CF & 11.57 & 3.03 & 4.30\\
    Other & 12.71 & 4.40 & 2.39\\
    CS & 20.63 & 14.17 & -1.50\\\bottomrule

  \end{tabular}
  \caption{Laughter impact by dialogue act group (SWDA, BERT), mean accuracy}
\end{table}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{img/SWDA-bertLvsNL.pdf}
  \caption{Change in accuracy for each SWDA dialogue act. Positive changes when adding laughter are shown in blue. Vertical bars indicate how often dialogue act is associated with laughter.}
    \label{fig:swda-by-da}
\end{figure*}

\begin{figure*}
  \label{fig:ami-by-da}
  \centering
  \includegraphics[width=\textwidth]{img/AMI-DA-bertLvsNL.pdf}
  \caption{Change in accuracy for each AMI dialogue act. Positive changes when adding laughter are shown in blue. Vertical bars indicate how often dialogue act is associated with laughter.}
\end{figure*}
% TODO per dialogue act analysis
% DONE compare impacts of CNN vs BERT
% DONE for both AMI and SWDA
% ?

@@

%\subsection{Experiment 4: Cross-domain pre-training (if time permits)} \label{sec:experiment4} % Bill
%  - cross-domain pre-training
\section{Related work} % add references first
Dialogue act recoginition
\begin{itemize}
  \item \citet{pragstVectorRepresentationUtterances2018} -- dialogue vector models. Uses vector-manual DA tag correspondance to argue for semantic relevance of their vector models (related to how we use DA tagging to verrify BERT usefulness)
  \item \citet{cerisaraEffectsUsingWord2vec2017} -- standard pre-trained word embeddings do not help for DAR in any of three tested languages (English, French, Czech)
  \item \citet{kalchbrennerRecurrentConvolutionalNeural2013} -- DAR model similar to our architecture. Uses an RNN ``discourse model'' and a CNN similar to our baseline encoder
  \item \citet{khanpourDialogueActClassification2016} -- Deep LSTM utt representation. No notion of context. Finds word vectors are useful.
  \item \citet{tranPreservingDistributionalInformation2017} -- Sequential DA prediction with uncertainty propegation
  \item \citet{chenDialogueActRecognition2017} -- SOTA? SWDA DAR using attention and CRF over utterances
  \item \citet{ortegaNeuralbasedContextRepresentation2017} -- SWDA DAR with attention-based context representations and CNN utterance representations
  \item \citet{shenNeuralAttentionModels2016} -- Uses attention for utt encoding in DAR. No notion of context, I think.
  \item \citet{tranHierarchicalNeuralModel2017} -- RNNs at both the utteranec and dialogue level. Also attention. Very similar to our architecture.
\end{itemize}
